\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
lock memory
print microsecond correctly

\documentclass[10pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{sectsty}
\usepackage{authblk}

\renewcommand{\refname}{}

@@

In our experiments, the kernel build were persistent in different SD/MMC media. The fact that different external storage devices have different access speeds could affect the final results. In order to eliminate the uncertainties and prevent the test process' pages from being swapped into disk, we locked all the test processes' pages inside memory. While using \textit{cyclictest} tool, we can achieve by specifying the '-m' option along with the command. On the other hand, we exclude the known latency factors and execute programs within one memory locking condition.

@@

From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 us) than on Xenomai-2(below 3 us). While this is not an occasional case(the same experiment was ran a couple times), we tried to look into the test code of latency to figure out the cause of this phenomenon.

\subsection{Experiment Result Analysis}
Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 us in idle situation, 18 us in stressed situation. And in the worse case, the latency is below 50 us. Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 us and can't guarantee a 50 us max latency (Actually in some cases the latency will exceed 100 us in stressed condition).  As for mainline Linux, the max latency easily exceeds 1 ms. When comparing the performance of Xenomai-3 to Xenomai-2, we can see that the stats in cyclictest and latency test is slightly better, except for the case of timer-irq latency in stressed condition.

>>>>

\documentclass[10pt,a4paper]{article}
\usepackage[english]{babel}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{sectsty}
\usepackage{authblk}
\usepackage{textcomp}
\renewcommand{\refname}{}

@@

In our experiments, the kernel build were persistent in different SD/MMC media. The fact that different external storage devices have different access speeds could affect the final results. In order to eliminate the uncertainties and prevent the test process' pages from being swapped into disk, we locked all the test processes' pages inside memory. While using \textit{cyclictest} tool, we can achieve by specifying the '-m' option along with the command. On the other hand, we exclude the known latency factors and execute programs within the memory-locked environment.

@@

From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai-3(over 3 \textmu s) than on Xenomai-2(below 3 \textmu s). While this is not an occasional case(the same experiment was ran a couple times), we tried to look into the test code of latency to figure out the cause of this phenomenon.

\subsection{Experiment Result Analysis}
Our data shows that the average user-level latency in either Xenomai 2 or 3 is around 9 \textmu s in idle situation, 18 \textmu s in stressed situation. And in the worse case, the latency is below 50 \textmu s. Meanwhile, the latency of PREEMPT\_RT has a user-level latency more than 20 \textmu s and can't guarantee a 50 \textmu s max latency (Actually in some cases the latency will exceed 100 us in stressed condition).  As for mainline Linux, the max latency easily exceeds 1 ms. When comparing the performance of Xenomai-3 to Xenomai-2, we can see that the stats in cyclictest and latency test is slightly better, except for the case of timer-irq latency in stressed condition.
